\plaintitle

### 2017-06-07 papers/IoT2017/intro.tex
final

In this paper, we assume the existence of the IoT infrastructure and specifically focus on the following privacy challenges.
%
%
% This is where the RIAPS and computing services discussion will be included. However, it does not solve the following challenges, which is the focus of this paper.
%
%\Abhishek{Can we merge this with last paragraph? It seems repetitive.}
%\Aron{I'll probably just remove this.}
%Specifically, 
%in order to take advantage of local energy production and storage capabilities, 
%in order to take advantage of these capabilities, 
%electric grids need to become more decentralized.
%However, a decentralized transactive energy system may pose a much greater threat to prosumers' privacy than existing smart metering systems.
%\Abhishek{We can introduce these bullets by stating that the privacy challenges specifically are (the privacy challenges were mentioned at the end of the paragraph above.)}
\begin{itemize}[itemsep=0.25\parskip,topsep=-0.5\parskip]
\item Firstly, since prosumers\footnote{We refer to customers as \emph{prosumers} to emphasize that they can not only consume energy, but may also produce it.}  may purchase energy from each other in a transactive microgrid, transactions may inadvertently reveal the prosumers' detailed energy usage patterns to other prosumers within the microgrid.
Addressing this issue in a decentralized trading system is quite challenging as it requires hiding the identities of trade partners from each other.
In comparison, secure smart metering reveals the prosumers' energy usage patterns \Abhishek{Earlier we mentioned the challenge of privacy with respect to system operator in the abstract. I think the system operator and provider are the same.  My question and comment were included in the abstract about this.} only to the provider. 
\item Secondly, \Abhishek{Is this not related to the first point? Perhaps the first point can be just about identity and second point can be specifically about consumption patterns.}\Aron{The first point is about to whom information might be leaked, and the second point is about the type of information. I'll make this more clear.} transactions may reveal the future energy usage of a prosumer, which could be used to infer private information.
For example, a smart home may know that its inhabitants will go out in the evening (e.g., by looking at their calendar), and it may trade energy futures accordingly in the morning.
Without adequate privacy measures, these trades may reveal to other prosumers in the microgrid that the inhabitants will not be at home later.
Note that energy futures, whose delivery may happen several hours after when the transaction is made, can play a very important role in predicting and controlling microgrid load.
In comparison, smart metering reveals only current (or past) usage.
\item Thirdly, transactions and energy usage data in a transactive microgrid are much richer sources of information than the simple energy usage data collected by smart meters.
More specifically, the information available in a transactive microgrid is a superset of what is available from smart metering, and it may be used to infer personal information, such as risk propensity and financial standing.
\end{itemize}
\vspace{0.5\parskip}

@@

\Abhishek{Can we cite an example of such a service?}
\Aron{I am not sure what you mean by ``such a service.''}
\Abhishek{We should connect the paper and our work back to IoT in this paragraph.}
In this paper, we propose a system that enables trading energy futures in a secure and verifiable manner, preserves the prosumers' privacy, and enables the DSO to regulate the trading platform and enforce certain safety rules.
\Aron{Since SIGCHI does not have section numbers, this paragraph, which describes the organization of the paper, is not very clear.}
First, we describe the basic components of a transactive microgrid, and we formulate security, safety, and privacy requirements. 
Then, we introduce a decentralized system for transactive microgrids based on distributed ledgers, and describe in detail the transactions and services that are used to implement this system.
Next, we discuss how the system satisfies the security, safety, and privacy requirements.
Finally, we give a brief overview of related work and offer concluding remarks.

>>>>

In this paper, we assume the existence of the IoT infrastructure and specifically focus on the following privacy challenges.
%
%
% This is where the RIAPS and computing services discussion will be included. However, it does not solve the following challenges, which is the focus of this paper.
%
%\Abhishek{Can we merge this with last paragraph? It seems repetitive.}
%\Aron{I'll probably just remove this.}
%Specifically, 
%in order to take advantage of local energy production and storage capabilities, 
%in order to take advantage of these capabilities, 
%electric grids need to become more decentralized.
%However, a decentralized transactive energy system may pose a much greater threat to prosumers' privacy than existing smart metering systems.
%\Abhishek{We can introduce these bullets by stating that the privacy challenges specifically are (the privacy challenges were mentioned at the end of the paragraph above.)}
\begin{itemize}[itemsep=0.25\parskip,topsep=-0.5\parskip]
\item Firstly, since prosumers\footnote{We refer to customers as \emph{prosumers} to emphasize that they can not only consume energy, but may also produce it.}  may purchase energy from each other in a transactive microgrid, transactions may inadvertently reveal the prosumers' detailed energy usage patterns to other prosumers within the microgrid.
Addressing this issue in a decentralized trading system is quite challenging as it requires hiding the identities of trade partners from each other.
In comparison, secure smart metering reveals the prosumers' energy usage patterns only to the operator. 
\item Secondly, \Abhishek{Is this not related to the first point? Perhaps the first point can be just about identity and second point can be specifically about consumption patterns.}\Aron{The first point is about to whom information might be leaked, and the second point is about the type of information. I'll make this more clear.} transactions may reveal the future energy usage of a prosumer, which could be used to infer private information.
For example, a smart home may know that its inhabitants will go out in the evening (e.g., by looking at their calendar), and it may trade energy futures accordingly in the morning.
Without adequate privacy measures, these trades may reveal to other prosumers in the microgrid that the inhabitants will not be at home later.
Note that energy futures, whose delivery may happen several hours after when the transaction is made, can play a very important role in predicting and controlling microgrid load.
In comparison, smart metering reveals only current (or past) usage.
\item Thirdly, transactions and energy usage data in a transactive microgrid are much richer sources of information than the simple energy usage data collected by smart meters.
More specifically, the information available in a transactive microgrid is a superset of what is available from smart metering, and it may be used to infer personal information, such as risk propensity and financial standing.
\end{itemize}
\vspace{0.5\parskip}

@@

\Abhishek{Can we cite an example of such a service?}
\Aron{I am not sure what you mean by ``such a service.''}
\Abhishek{We should connect the paper and our work back to IoT in this paragraph.}
In this paper, we propose a solution that enables trading energy futures in a secure and verifiable manner, preserves the prosumers' privacy, and enables the DSO to regulate the trading platform and enforce certain safety rules.
\Aron{Since SIGCHI does not have section numbers, this paragraph, which describes the organization of the paper, is not very clear.}
First, we describe the basic components of a transactive IoT microgrid, and we formulate security, safety, and privacy requirements. 
Then, we introduce a decentralized system for transactive microgrids based on distributed ledgers, and describe in detail the transactions and services that are used to implement this system.
Next, we discuss how the system satisfies the security, safety, and privacy requirements.
Finally, we give a brief overview of related work and offer concluding remarks.

### 2017-06-07 papers/IoT2017/paper.tex
no message
final

% Paper metadata (use plain text, for PDF inclusion and later
% re-using, if desired).  Use \emtpyauthor when submitting for review
% so you remain anonymous.
\def\plaintitle{Private Blockchains for Transactive Energy:\\Security, Privacy, and Safety}
\def\plainauthor{First Author, Second Author, Third Author}
\def\emptyauthor{}
\def\plainkeywords{Internet of Things; blockchain; transactive energy; privacy; security; transactive microgrid; smart grid; anonymity.}
\def\plaingeneralterms{Design, Human Factors, Reliability, Security} % TODO: revise

@@

\begin{abstract}
Power grids are undergoing major changes due to rapid growth in renewable energy resources and improvements in battery technology.
While these changes enhance sustainability and efficiency, they also create significant management challenges as the complexity of power systems increases.
To tackle these challenges, decentralized IoT solutions are emerging, which may arrange local communities into transactive microgrids.
Within a transactive microgrid, consumers with energy generation and storage capabilities may trade energy with each other, thereby smoothing the load on the main grid using local supply.
However, providing security, safety, and privacy in a decentralized and transactive energy system is very challenging.
On the one hand, consumers' personal information must be protected from their trade partners and
\Abhishek{To what extent is this different that the information already known by the system operator? Is this more related to the ``real-time'' nature of transactive information? Rather than aggregative total information which is available at the end of billing cycle today.} \Aron{Do we need to detail this in the abstract?}\Abhishek{we dont have to} the system operator.
On the other hand, the system must be protected from careless or malicious trading, which could destabilize the entire grid. 
In this paper, we design a secure and safe solution for transactive microgrids, which enables consumers to trade energy without sacrificing their privacy.
Our solution builds on distributed ledgers, such as blockchains, and provides anonymity for communication, bidding, and trading.
\end{abstract}

>>>>

% Paper metadata (use plain text, for PDF inclusion and later
% re-using, if desired).  Use \emtpyauthor when submitting for review
% so you remain anonymous.
\def\plaintitle{Providing Privacy, Safety, and Security in IoT-Based Transactive Energy Systems}
\def\plainauthor{First Author, Second Author, Third Author}
\def\emptyauthor{}
\def\plainkeywords{Internet of Things; blockchain; transactive energy; privacy; security; transactive microgrid; smart grid; anonymity.}
\def\plaingeneralterms{Design, Human Factors, Reliability, Security} % TODO: revise

@@

\begin{abstract}
Power grids are undergoing major changes due to rapid growth in renewable energy resources and improvements in battery technology.
While these changes enhance sustainability and efficiency, they also create significant management challenges as the complexity of power systems increases.
To tackle these challenges, decentralized IoT solutions are emerging, which may arrange local communities into transactive microgrids.
Within a transactive microgrid, consumers with energy generation and storage capabilities can trade energy with each other, thereby smoothing the load on the main grid using local supply.
However, providing security, safety, and privacy in a decentralized and transactive energy system is very challenging.
On the one hand, consumers' personal information must be protected from their trade partners and
\Abhishek{To what extent is this different that the information already known by the system operator? Is this more related to the ``real-time'' nature of transactive information? Rather than aggregative total information which is available at the end of billing cycle today.} \Aron{Do we need to detail this in the abstract?}\Abhishek{we dont have to} the system operator.
On the other hand, the system must be protected from careless or malicious trading, which could destabilize the entire grid. 
In this paper, we design a secure and safe solution for transactive microgrids, which enables consumers to trade energy without sacrificing their privacy.
Our solution builds on distributed ledgers, such as blockchains, and provides anonymity for communication, bidding, and trading.
\end{abstract}

### 2017-06-07 papers/IoT2017/related.tex
final

%\subsection{Smart Grid and Meter Privacy}
% http://ieeexplore.ieee.org/abstract/document/5054916/
%McDaniel and McLaughlin discuss privacy challenges in smart grids~\cite{mcdaniel2009security}.
% https://arxiv.org/pdf/1108.2234.pdf
% https://pdfs.semanticscholar.org/cdf8/a5b6256823bca38a1d2347ab36f8e4a2ca94.pdf
% http://www.comm.toronto.edu/~akhisti/sm.pdf
% https://www.researchgate.net/profile/Georgios_Kalogridis/publication/224189766_Smart_Grid_Privacy_via_Anonymization_of_Smart_Metering_Data/links/541169510cf2b4da1bec4193.pdf
% https://arxiv.org/pdf/1305.0735.pdf
New privacy concerns arise with the continuing adoption of smart grids. In addition to both old and new security threats, such as energy theft and smart meter malware, McDaniel and McLaughlin discuss the privacy concerns of energy usage profiling that smart grids could potentially enable~\cite{mcdaniel2009security}. Several approaches have been investigated as potential means to provide privacy protections for smart grid users.

Some approaches look to the use of protocols and/or frameworks to help protect privacy. Rajagopalan et al.\ use tools from information theory to present a framework, which abstracts both the privacy and the utility requirements of smart meter data~\cite{rajagopalan2011smart,sankar2013smart}. Their framework leads to a novel tractable privacy-utility tradeoff problem with minimal assumptions. Efthymiou and Kalogridis describe a method for securely anonymizing frequent electrical metering data sent by a smart meter~\cite{efthymiou2010smart}. Their approach is based on the observation that frequent metering data may be required by an energy distribution network for operational reasons, but it may not necessarily need to be attributable to a specific smart meter. The authors describe a method that provides a third-party escrow mechanism for authenticated anonymous meter readings, which are difficult to associate with particular smart meter.

Additionally, other approaches such as additional hardware components are explored for potential privacy gains. Varodayan and Khisti study using rechargeable battery for partially protecting the privacy of information contained in a household's electrical load profile~\cite{varodayan2011smart}. They show that stochastic battery policies may leak 26\% less information than a best-effort policy, holds the output load constant whenever possible. Tan et al. study privacy in a smart metering system from an information theoretic perspective in the presence of energy harvesting and storage units~\cite{tan2013increasing}. They show that energy harvesting provides increased privacy by diversifying the energy source, while a storage device can be used to increase both energy efficiency and privacy. They show that there exists a trade-off between the information leakage rate and the wasted energy rate, and study the impact of the energy harvesting rate and the size of the storage device on this trade-off.

Our solution extends earlier work by considering a decentralized IoT system for transactive energy, and addressing the novel privacy threat posed by trading. In other words, while earlier results protected prosumers' privacy from the DSO, we protect privacy from other prosumers as well as from outside attackers.

A key element of our approach is the ability to distribute the informtion among peers. For that purpose, we rely on the use of Blockchains. 
As Blockchain technology continues to develop and mature, new frameworks, services, and protocols are being developed to leverage blockchain's distributed ledger. Hyperledger Fabric is a platform for distributed ledger solutions, which was designed to support pluggable implementations of different components~\cite{hyperledger2017fabric}. Bitcoin Lightning Network is decentralized system, in which transactions are sent over a network of micropayment channels whose transfer of value occurs off-blockchain~\cite{poon2016bitcoin}. However, this paper focuses on theoretical aspects of our implementation and as such any one of these distributed ledgers provide the required capabilities.\Abhishek{Aron please see this paragraph}

>>>>

%\subsection{Smart Grid and Meter Privacy}
% http://ieeexplore.ieee.org/abstract/document/5054916/
%McDaniel and McLaughlin discuss privacy challenges in smart grids~\cite{mcdaniel2009security}.
% https://arxiv.org/pdf/1108.2234.pdf
% https://pdfs.semanticscholar.org/cdf8/a5b6256823bca38a1d2347ab36f8e4a2ca94.pdf
% http://www.comm.toronto.edu/~akhisti/sm.pdf
% https://www.researchgate.net/profile/Georgios_Kalogridis/publication/224189766_Smart_Grid_Privacy_via_Anonymization_of_Smart_Metering_Data/links/541169510cf2b4da1bec4193.pdf
% https://arxiv.org/pdf/1305.0735.pdf
New privacy concerns arise with the continuing adoption of smart grids. In addition to both old and new security threats, such as energy theft and smart-meter malware, McDaniel and McLaughlin discuss the privacy concerns of energy usage profiling that smart grids could potentially enable~\cite{mcdaniel2009security}. Several approaches have been investigated as potential means to provide privacy protections for smart grid users.

Some approaches look to the use of protocols and/or frameworks to help protect privacy. Rajagopalan et al.\ use tools from information theory to present a framework, which abstracts both the privacy and the utility requirements of smart-meter data~\cite{rajagopalan2011smart,sankar2013smart}. Their framework leads to a novel tractable privacy-utility tradeoff problem with minimal assumptions. Efthymiou and Kalogridis describe a method for securely anonymizing frequent electrical metering data sent by a smart meter~\cite{efthymiou2010smart}. Their approach is based on the observation that frequent metering data may be required by an energy distribution network for operational reasons, but it may not necessarily need to be attributable to a specific smart meter. The authors describe a method that provides a third-party escrow mechanism for authenticated anonymous meter readings, which are difficult to associate with a particular smart meter.

Additionally, other approaches such as additional hardware components are explored for potential privacy gains. Varodayan and Khisti study using a rechargeable battery for partially protecting the privacy of information contained in a household's electrical load profile~\cite{varodayan2011smart}. They show that stochastic battery policies may leak 26\% less information than a best-effort policy, which holds the output load constant whenever possible. Tan et al.\ study privacy in a smart metering system from an information theoretic perspective in the presence of energy harvesting and storage units~\cite{tan2013increasing}. They show that energy harvesting provides increased privacy by diversifying the energy source, while a storage device can be used to increase both energy efficiency and privacy. % They show that there exists a trade-off between the information leakage rate and the wasted energy rate, and study the impact of the energy harvesting rate and the size of the storage device on this trade-off.

Our solution extends earlier work by considering a decentralized IoT system for transactive energy, and addressing the novel privacy threat posed by trading. In other words, while earlier results protected the prosumers' privacy from the DSO, we protect privacy from other prosumers as well as from outside attackers.

A key element of our approach is the ability to distribute information among peers. For that purpose, we rely on the use of blockchains. 
As blockchain technology continues to develop and mature, new frameworks, services, and protocols are being developed to leverage blockchain's distributed ledger. Hyperledger Fabric is a platform for distributed ledger solutions, which was designed to support pluggable implementations of different components~\cite{hyperledger2017fabric}. Bitcoin Lightning Network is decentralized system, in which transactions are sent over a network of micropayment channels, whose transfer of value occurs off-blockchain~\cite{poon2016bitcoin}. However, this paper focuses on theoretical aspects of our implementation and as such, any one of the distributed ledgers provide the required capabilities.

### 2017-06-07 papers/IoT2017/services.tex
final

\subsubsection{Transaction Anonymity}
Communication anonymity is necessary for anonymous trading, but it is not sufficient: if prosumers used their own accounts to transfer assets, trades would not be anonymous.
Fortunately, most distributed ledgers allow users to easily generate new addresses\footnote{The usage of the term \emph{address} varies between distributed ledgers, but our system could be implemented using any popular ledger, such as Bitcoin and Ethereum. 
Specifically, we use the term address to denote a possible destination for asset transfers. 
Assets transferred to an address can be used only by someone who knows the private key of the address (typically, the one who generated the address).} 
at random.
Since these addresses are generated randomly, they are anonymous in the sense that no one can tell who generated them.
However, if prosumers simply transferred assets to these addresses, they could be easily de-anonymized by tracing the assets back to the prosumers.

>>>>

\subsubsection{Transaction Anonymity}
Communication anonymity is necessary for anonymous trading, but it is not sufficient: if prosumers used their own accounts to transfer assets, trades would not be anonymous.
Fortunately, most distributed ledgers allow users to easily generate new addresses %\footnote{The usage of the term \emph{address} varies between distributed ledgers, but our system could be implemented using any popular ledger, such as Bitcoin and Ethereum. 
%Specifically, we use the term address to denote a possible destination for asset transfers. 
%Assets transferred to an address can be used only by someone who knows the private key of the address (typically, the one who generated the address).} 
at random.
Since these addresses are generated randomly, they are anonymous in the sense that no one can tell who generated them.
However, if prosumers simply transferred assets to these addresses, they could be easily de-anonymized by tracing the assets back to the prosumers.

### 2017-06-07 papers/IoT2017/solution.tex
final

\begin{figure}[h!]
\center
\begin{tikzpicture}[x=8cm, y=0.8cm, font=\small,
  nodeStyle/.style={rounded corners=0.1cm, drop shadow={shadow xshift=0.05cm, shadow yshift=-0.05cm, fill=black}}
]
%\draw [nodeStyle, fill=white]   (0, 0) rectangle    (1, 0.9) node [midway, align=center] {Communication network\\[-0.2em]and operating system};

@@

At this point, the production asset can still be traced back to the prosumer since the ledger is public.
To achieve anonymity, the prosumer uses a \emph{mixing service}, which in practice may be implemented as a decentralized protocol, such as CoinShuffle~\cite{ruffing2014coinshuffle} or Xim~\cite{bissias2014sybil}.
The prosumer transfers the production asset to the mixing service using an \emph{energy and financial transaction} \circled{2}, which is also recorded on the distributed ledger.
In turn, the mixing service transfers the production asset to an \emph{anonymous address} \circled{3}\Aron{We should probably insert a good definition here for readers who are unfamiliar with blockchain transactions.}, which is randomly generated and controlled by the prosumer.
Since the mixing service transfers assets from multiple prosumers to multiple anonymous addresses at the same time, and the anonymous addresses were generated at random by the prosumers, the assets cannot be traced back to the original prosumers after mixing.\footnote{Note that prosumers should divide their assets between multiple anonymous addresses; otherwise, each asset might be traced back to its prosumer based on the amount of energy that it contains.}

>>>>

\begin{figure}[h!]
\center
\begin{tikzpicture}[x=8cm, y=1.1cm, font=\small,
  nodeStyle/.style={rounded corners=0.1cm, drop shadow={shadow xshift=0.05cm, shadow yshift=-0.05cm, fill=black}}
]
%\draw [nodeStyle, fill=white]   (0, 0) rectangle    (1, 0.9) node [midway, align=center] {Communication network\\[-0.2em]and operating system};

@@

At this point, the production asset can still be traced back to the prosumer since the ledger is public.
To achieve anonymity, the prosumer uses a \emph{mixing service}, which in practice may be implemented as a decentralized protocol, such as CoinShuffle~\cite{ruffing2014coinshuffle} or Xim~\cite{bissias2014sybil}.
The prosumer transfers the production asset to the mixing service using an \emph{energy and financial transaction} \circled{2}, which is also recorded on the distributed ledger.
In turn, the mixing service transfers the production asset to an \emph{anonymous address} \circled{3}%\Aron{We should probably insert a good definition here for readers who are unfamiliar with blockchain transactions.}
, which is randomly generated and controlled by the prosumer.\footnote{The usage of the term \emph{address} varies between distributed ledgers, but our system could be implemented using any popular blockchain, such as Bitcoin and Ethereum. 
Specifically, we use the term address to denote a possible destination for asset transfers. 
Assets that have been transferred to an address can be used only by someone who ``controls'' the address (typically, the one who generated it), which usually means knowing a private key that corresponds to the address.} % knows the private key of the address (typically, the one who generated the address).} 
Since the mixing service transfers assets from multiple prosumers to multiple anonymous addresses at the same time, and the anonymous addresses were generated at random by the prosumers, the assets cannot be traced back to the original prosumers after mixing.\footnote{Note that prosumers should divide their assets between multiple anonymous addresses; otherwise, each asset might be traced back to its prosumer based on the amount of energy that it contains.}
